### 2014-06-06 paper/body.tex
edited caption of Fig 1 to include the new treatment names

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{Overview of the experimental treatments and controls. \emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \citep{Krizhevsky-2012}. Training occurs on only half the dataset (e.g. dataset A) for consistency with the experimental treatments. The baseline control is repeated for each half of the dataset (A and B). The labeled rectangles (e.g. $W_{A1}$) represent the weight vector for that layer. That the rectangle is colored indicates that the weight layer has been trained on the dataset of that color (e.g. dataset A). The vertical, ellipsoidal bars represent neural activations that occur when the network is activated. \emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern). The weights of the first $N$ layers of the network are locked, meaning they do not change during training. The remaining layers are trained as normal on half the dataset. A replicate (not pictured) is performed on the other half of the dataset. \emph{Fourth row:} The ``selfer network'' control. In this control the first $N$ weight layers of the network are copied from a base network (e.g. one trained on dataset B) and then the entire network is trained on that same dataset (in this example, dataset B). These layers are either locked during training (in the ``locked selfer treatments'') or allowed to train as usual (in the ``released selfer treatments''. The weights of layers after the first $N$ layers are initialized randomly and then allowed to train as usual. This treatment tests whether filters at different layers need to co-adapt during training, or if they can be trained asynchronously. \emph{Fifth row:} The ``transfer network'' experimental treatment. Same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g. B) and then the entire network is trained on the \emph{other} half of the dataset (e.g. dataset A). This treatment tests transfer learning.}
\label{fig:transfer}
\end{figure}

>>>>

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{Overview of the experimental treatments and controls. \emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \citep{Krizhevsky-2012}. Training occurs on only half the dataset (e.g. dataset A) for consistency with the experimental treatments. The baseline control is repeated for each half of the dataset (A and B). The labeled rectangles (e.g. $W_{A1}$) represent the weight vector for that layer. That the rectangle is colored indicates that the weight layer has been trained on the dataset of that color (e.g. dataset A). The vertical, ellipsoidal bars represent neural activations that occur when the network is activated. \emph{Third row:} In this control, the weights (filters) of all layers are initialized randomly (checkered pattern). The weights of the first $N$ layers of the network are frozen (locked), meaning they do not change during training. The remaining layers are trained as normal on half the dataset. A replicate (not pictured) is performed on the other half of the dataset. \emph{Fourth row:} The ``selfer network'' control. In this control the first $N$ weight layers of the network are copied from a base network (e.g. one trained on dataset B) and then the entire network is trained on that same dataset (in this example, dataset B). These layers are either locked during training (in the ``frozen selfer treatments'') or allowed to further fine-tune on the new data set (in the ``fine-tuned selfer treatments''), meaning that normal training occurs in those layers after initialization. The weights of layers after the first $N$ layers are initialized randomly and then allowed to train normally. This treatment tests whether filters at different layers need to co-adapt during training, or if they can be trained asynchronously. \emph{Fifth row:} The ``transfer network'' experimental treatment is the same as the selfer network treatment, except that the first $N$ layers are copied from one half of the dataset (e.g. B) and then the entire network is trained on the \emph{other} half of the dataset (e.g. dataset A). This treatment tests transfer learning.}
\label{fig:transfer}
\end{figure}
